Unit tests

### 2018-03-08 Tests.Rmd
tests of the skewness and 3rd central moment function added

```{r}
source("SkewnessAnd3CentMom.R")
#Dan fill in - see if there is testing text in the file itself 
```

>>>>

Test for unbiased estimator of third central moment:
```{r test_myskewness, echo=F, cache=T, cache.extra=list(mtime("SkewnessAnd3CentMom.R"))}
source("SkewnessAnd3CentMom.R")
set.seed(101)

x<-rnorm(100000)
my3cm(x) #should be close to 0

x<-rpois(100000,5)
my3cm(x) #should be close to 5, but not necessarily super close
#since 3rd moments are hard to estimate accurately

#see if it appears unbaised
res<-NA*numeric(1000)
for (counter in 1:1000)
{
  x<-rpois(100000,5)
  res[counter]<-my3cm(x) 
}
hist(res)
mean(res)
```

No need to test the accompanying skewness function, since it is such a simple extension of the above.
